---
title: "Optimal stepped-wedge cluster randomised trial design"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
params:
  C:                       NA
  Ti:                      NA
  m:                       NA
  rho0:                    NA
  r:                       NA
  extreme_seq:             NA
  time_effect:             NA
  optimal_num_exact:       NA
  optimal_num_rounded:     NA
  optimal_weights_exact:   NA
  optimal_weights_rounded: NA
  exact_equal:             NA
  exact_weighted:          NA
  rounded:                 NA
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r params, echo = FALSE, results = "asis"}
C                       <- params$C
Ti                      <- params$Ti
m                       <- params$m
rho0                    <- params$rho0
r                       <- params$r
extreme_seq             <- params$extreme_seq
time_effect             <- params$time_effect
optimal_num_exact       <- params$optimal_num_exact
optimal_num_rounded     <- params$optimal_num_rounded
optimal_weights_exact   <- params$optimal_weights_exact
optimal_weights_rounded <- params$optimal_weights_rounded
```

```{r input_text, echo = FALSE, results = "asis"}
if (extreme_seq) {
  extreme_seq_text <- "will"
} else {
  extreme_seq_text <- "will not"
}
if (time_effect == "discrete") {
  time_effect_text <- "discrete fixed effects"
} else if (time_effect == "linear") {
  time_effect_text <- "a linear function"
} else if (time_effect == "quadratic") {
  time_effect_text <- "a quadratic function"
} else if (time_effect == "linear") {
  time_effect_text <- "a cubic function"
} else if (time_effect == "linear") {
  time_effect_text <- "a quadratic function"
} else if (time_effect == "linear") {
  time_effect_text <- "a quintic function"
}
```

# Inputs

The following choices were made:

- The number of clusters will be $C = \boldsymbol{`r C`}$.
- The number of time periods will be $T = \boldsymbol{`r Ti`}$.
- The number of measurements per cluster-period will be $m = \boldsymbol{`r m`}$.
- The within-period intra-cluster correlation will be $\rho_0 = \boldsymbol{`r rho0`}$.
- The autoregressive structure parameter will be $r = \boldsymbol{`r r`}$.
- Time effects will be modelled using __`r time_effect_text`__.
- Sequences of all control/all intervention allocation __`r extreme_seq_text`__ be allowed.

# Outputs

- The exact optimal weights to assign to each sequence are $\boldsymbol{(`r paste(round(optimal_weights_exact, 3), collapse = ", ")`)}$.
- The exact optimal number of clusters to assign to each sequence are $\boldsymbol{(`r paste(round(optimal_num_exact, 3), collapse = ", ")`)}$.
- The rounded optimal weights to assign to each sequence are $\boldsymbol{(`r paste(round(optimal_weights_rounded, 3), collapse = ", ")`)}$.
- The rounded optimal number of clusters to assign to each sequence are $\boldsymbol{(`r paste(round(optimal_num_rounded, 3), collapse = ", ")`)}$.

# Plots

```{r, echo = FALSE, results = "asis", dpi = 600}
print(params$exact_equal)
cat("\n \n \n \n \n \n")
print(params$exact_weighted)
cat("\n \n \n \n \n \n")
print(params$rounded)
```
